%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}


% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }



%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Mikhail Krutikhin} \\[7.5pt]
\href{https://github.com/winte256}{\raisebox{-0.05\height}\faGithub\ Winte256} \ $|$ \ 
\href{https://linkedin.com/in/mikhail-krutikhin}{\raisebox{-0.05\height}\faLinkedin\ mikhail-krutikhin} \ $|$ \ 
% \href{https://mysite.com}{\raisebox{-0.05\height}\faGlobe \ mysite.com} \ $|$ \ 
\href{mailto:m.krutihin@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ m.krutihin@gmail.com} \ $|$ \ 
\href{tel:+381621150562}{\raisebox{-0.05\height}\faMobile \ +381 62 1150 562} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
\section{Summary}
Has 6+ years of programming experience, 5+ years of specialized experience in frontend, 3+ years of Team Leadership (3+ ppl). Uses Next.js and Nuxt.js

Technical Skills: Javascript/Typescript, React.js, Vue.js, Node.js, HTML, CSS, GIT etc.

Expirienced with Algorithms and data structures.

Recent personal achievement: Initiated and orchestrated the formation of a small group within the company, dedicated to enhancing our Computer Science knowledge.

%Experience
\section{Work Experience}

\begin{joblong}{Digital Wave Technology}{Nov 2023 - Present}
  \item /Stack/: {Vue, Pinia, Node.js, graphQL}
{\fontsize{13.2pt}{14.6pt}\selectfont
  \item[*] Key Responsibilities:
    \begin{itemize}
      \item[--] Pricing system development;
      \item[--] Discussing product requirements with the CEO;
      \item[--] Conducting code reviews for colleagues;
      \item[--] Deep involvement in a unique product; 
      \item[--] Developing components based on clients' requirements; 
      \item[--] Fixing bugs on the frontend as well as the backend; 
      \item[--] Participating in coding interviews;
    \end{itemize}

  \item[*] Achievements:
    \begin{itemize}
      \item[--] Investigated Camunda environment and integrated it with our system;
      \item[--] Developed a fully custom control panel for Camunda Modeler;
      \item[--] Developed many complicated components like search with autocomplete.
    \end{itemize}
}
\end{joblong}

\begin{joblong}{DEXART}{Jul 2022 - Nov 2023}
  \item /Stack/: {Vue, Nuxt, Vercel, Git, CI/CD, OAuth, web3, SSR, BFF}

  \item [*] Team and Role Context:
\begin{itemize}
  \item [--] Key developer in a compact frontend team, consisting of fewer than 5 professionals. 
  \item [--] Tasked with the coordination and assignment of frontend-specific duties among a three-person subset of the larger team.
  \item [--] Regular connect with backend specialists to ensure seamless integration and functionality.
\end{itemize}

  \item [*] Key Responsibilities:
\begin{itemize}
  \item [--] Managed the development and maintenance of a 2D map interface in Unity
  \item [--] Successfully rolled out the dex.art project within stipulated timelines.
  \item [--] Engineered a unified system for user authentication and registration, leveraging OAuth, web3, and standard credential methodologies.
  \item [--] Developed multi-language support (in excess of five languages), resulting in a twofold surge in advertisement conversions.
\end{itemize}


  \item [*] Achievements:
\begin{itemize}
  %\item [--] Strategically transitioned the project to a serverless environment via Vercel, leading to substantial reductions in the overheads associated with Backend-For-Frontend (BFF) upkeep.
  \item [--] Played a pivotal role in the transition from Nuxt 2 to Nuxt 3, ensuring continuity and efficiency.
%  \item [--] Pioneered the automation of review processes within the frontend department using GitHub actions, enhancing productivity and consistency.
  \item [--] Played a pivotal role in enhancing the application's performance, significantly reducing bundle sizes and accelerating website load times.
\end{itemize}

\end{joblong}

\begin{joblong}{OTON Technology}{Dec 2017 - Jul 2022}
  \item /Stack/: {React, Next, Vue.js, Node.js, pm2}
  \item [*] Main Tasks:
    \begin{itemize}
      \item [--] Develop and maintane new frontend solution for manage network  business on the web3 technologies.
      \item [--] Make a web store which support server-side rendering and ready to high load of visitors.
      \item [--] Backend Collaboration: Maintained a continuous dialogue with the backend team to craft cohesive and robust solutions in tandem with frontend requirements.
    \end{itemize}

  \item [*] Results:
      \begin{itemize}
      \item [--] Successfully developed back office frontend solution using React.js on a client and simple static node.js server on a backend which was later transitioned to Vue and some cloud solution for backend. It boosted stability and  expedited feature development.
      \item [--] Oton Market was a big and interesting project and after we finished this project we closed all business requests. I got 2 junior frontend developers in my team. 
        \end{itemize}
\end{joblong}

\begin{joblong}{TradeSoft Company}{May 2017 - Dec 2017}
  \item[*] Context
    \begin{itemize}
      \item [--] Junior frontend developer
      \item [--] Studied some technologies like: Vue.js, Docker, Linux, REST API, CI/CD, agile methodology and tests.
      \item [--] Collaborated with the backend team to address frontend requirements and integration points.
    \end{itemize}
  
  \item [*] Results:
    \begin{itemize}
      \item [--] Played a key role in enhancing the "Parts-Catalogs" frontend, resulting in a more interactive and user-friendly product.
      \item [--] Demonstrated significant growth and skill acquisition in a challenging and fast-paced environment.
      \item [--] Contributed to the project's overall success, with "Parts-Catalogs" witnessing increased usability and customer satisfaction during my tenure.
    \end{itemize}
\end{joblong}
  
%Projects
\section{Projects}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Some Project} & \hfill \href{}{} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{The result of my work in Dexart company. Has over than 20k users every day.  Technology frontend foundation is Nuxt+Vercel. Recently was refactored to latest Nuxt.js version and optimized for high load}  \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}	
2014 - 2016 & Diploma in Information Technology (Incomplete) at \textbf{Kirov Aviation College} \hfill \normalsize  \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Some Skills &  \normalsize{Typescript, Javascript, React, Vue, Next, Nuxt, HTML, CSS, REST, SSR, Algorithms, OAuth, BFF, mobx etc.}\\
Some More Skills  &  \normalsize{English(B1), Russian(Native), Problem-solving, Self-Motivated etc.}\\  
\end{tabularx}

\vfill
\center{\footnotesize Last updated: \today}

\end{document}
